\paragraph{}
This is an essay on the paper `A Metrics Suite for Object Oriented Design' \autocite{METRICS_SUITE} by S. Chidamber and C.
Kermerer which is dated from June 1994. First there will be a brief summary about the paper itself followed by
its merits and drawbacks. The second used to write this essay is
`Quality Analysis of Object Oriented Cohesion Metrics' by P. Joshi and R. K. Joshi \autocite{JOSHI}.
Although the second paper did not directly relate to the subject paper, it gave enough insight to perform more research
on the drawbacks of `A Metrics Suite for Object Oriented Design'.

\paragraph{}
When object oriented design (OOD) starts to unfold in the industry, the need for feedback on this kind of software
development increases. The writers address the problems that cause the need for a metrics suite that provides the
required feedback on OOD. The existing metrics lack the theoretical ground, are not sufficient for OOD,
technology dependent or too labor-intensive to collect.
The paper introduces six metrics as a suite: Weighted Methods Per Class (WMC), Depth of Inheritance Tree (DIT),
Number of Children (NOC), Coupling between object classes (CBO), Response For a Class (RFC) and Lack of
Cohesion of Methods (LCOM). These metrics are assessed with the software complexity metric properties introduced by
Weyuker \autocite{WEYUKER} and found to comply with most of the specified properties.
Criticism on previous research was the lack of theoretical basis, which is refuted on by the use of the
model provided by Weyuker, and lack of empirical data, which is added by applying the metrics on two different OO
applications (C++ and Smalltalk) using an automated tool. The main contribution of the paper can be summarized as a
suite of six individual software complexity metrics that can be combined to illuminate design problems and/or choices
within an OOD.

\paragraph{}
The paper is well structured and meets the expectations from the reader. Where the writers introduce the problem
(section II), they succeed this with separate sections on the point of view and approach. First the writers show how they
approaches the properties introduced by OOD and which metrics were abstracted (section III), secondly they shows how the
lack of theoretical ground is tackled in this research (section IV) and ends this with a presentation of the empirical
data collection (section V). Section VI contains the research results. The writers iterate over different metrics and
accompany each metric with a point of view, perform an analytical evaluation and present the empirical data and its
interpretation. This section concludes with a summary. The paper ends with the concluding remarks.

\paragraph{}
While the paper does not contain a research question the writers state a clear research problem, which is actually tackled.
The problem is divided in two parts. The first is the lack of metrics that relate to the properties that emerge from an
OOD, which indicate the need for such metrics. The second part concentrates on the theoretical criticism of metrics
applied to conventional non-OO applications. Focussing on the second part, this is the argument to include a theoretical base in the
research, but the provided substantiating research introduced by the writers merely focus on complexity metrics instead
of metrics in general. The writers lack to explicitly scope the research to complexity metrics, but abide to this
point of view throughout the rest of the paper. With the constructive use of complexity as point of view and the use of
a theoretical basis that reflected on the complexity measures by Weyuker, the writers should have addressed this scope in
the title, abstract or introduction of the paper. Also the writers do not introduce the concept of complexity. The concept of
software complexity can be interpreted in different ways such as the difference of metrics introduced by McCabe \autocite{ICSE-1976-McCabe}
and Henry \autocite{HENRY}.

\paragraph{}
The writers argue, as mentioned above, that existing metrics do not relate to the properties of OOD, but they fail
to demonstrate this or refer to previous works that indicate this. Although the reader can assume the lack of these
metrics due to the maturity of object oriented development in the industry at that time, the writers should have introduced
their assumptions or have added references to previous work that indicate this. The previous works that are referenced include suggestions
and attempts for OOD metrics, but these sources do not address the missing relation of existiting metrics with the OOD
properties, nor do the writers.

\paragraph{}
In the most important section of the paper the writers iterate over each proposed metric. The writers apply the
same pattern for each metric, which implicitly sets the expectation for the reader. For each metric the writers give a
clear definition, theoretical basis and point of view. The description and the theoretical basis give the definition and
motivation for the metric. The point of view of each metric adds a more vivid argument for the need of each metric.
Some of these arguments are more application-type specific. For example: ``The larger the number of methods that can be
invoked from a class, the greater the complexity of the class.'' I cannot reason about the types of application that were
developed at the time of the paper, but in the present day there are a lot of APIs that separate their data from their
logic. Although this is a more procedural approach than OO, it is applied with OO languages. The method count
with these designs is higher in the data objects while they tend to be much simpler than the code in the domain-specific
layer of an application. Aside from a few questionable point of views, the arguments the author makes are solid.
Where the point of view of the paper is convincing, the theoretical basis lacks detail on a few points. For example:

\begin{itemize}
\item
The definition of the NOC metric states: ``number of immediate subclasses subordinated of a class in the class
hierarchy'', but the theoretical basis states: ``it is a measure of how many subclasses are going to inherit
the methods of the parent class''. The number of inheriting classes is not equal to the number of immediate subclasses of a
class.
\item
The LCOM metric is a computation based on the intersection of accessed fields of two methods. To identify two
methods with or without accessed field similarity, the writers use the notion of pairs. These pairs however are
computed using the Cartesian product of a list containing field access sets (which are mapped from the
methods). The Cartesian product holds the reflexive relational property, which by definition will decrease
the outcome with at least the number of elements in the set consisting of the field access sets.
The theoretical basis of LCOM states ``the larger the number of similar methods, the more cohesive the class'',
but a simple counter example shows that there is a bug in the definition. Assume we have a set of instance
variables: $\{I_1, I_2\}$ and a set of methods $\{M_1, M_2\}$ where $M_1$ uses $I_1$ and $M_2$ uses $I_2$, then from
the LCOM definition, $P = \{( \{I_1\}, \{I_2\} ), ( \{I_2\}, \{I_1\} ) \}$ and
$Q = \{( \{I_1\}, \{I_1\} ), ( \{I_2\}, \{I_2\} ) \}$. This results in a LCOM value of $0$ that indicates that
the class is most cohesive, but $M_1$ and $M_2$ do not relate in a single matter. This problem is presented in other
works such as Basisi et al. \autocite{BASILI} and Chai et al. \autocite{CHAE}.
\end{itemize}

\paragraph{}
These points show that there is no sound symbiosis between the definition and the application.

\paragraph{}
After each metric is made clear the writers give an analytical evaluation of the metric and presents the empirical
data. The analytical evaluation is a formal proof, which indicates that each metric complies to the metric properties
specified by Weyuker.

\paragraph{}
The writers summarize the result in the last part of the paper, but also introduce new concepts on how the metrics
combined could be used as design indicators, why some properties of the metrics model are not met and the reason for this, and the
future direction to research the subject matter. I would rather have seen this in separate sections, mainly due to the reason that these
components deserve their own section. The introduced point of views on combined metrics is one of the main contributions
of the paper as it has a closer relation to OOD than the individual metrics.

\paragraph{}
The contribution of the paper to the field of software engineering is tremendous. A lot of researchers used the paper
as basis for their research or simply as reference material. Mainly the cohesion metric has been researched a lot (possibly
due to the demonstrated problem and researchers trying to fix this). In literature it is commonly known that there are
different LCOM versions (1 up to 5) \autocite{TOOLS-USA-2003-BadriB04}, which shows the extension on the initial contribution. Todays research
tends to focus less on developing new metrics, but instead focus more on how to apply the existing metrics. For example:

\begin{itemize}
\item the quality of cohesion metrics \autocite{DESOUKY} \autocite{JOHARI},
\item comparison between different cohesion metrics \autocite{JOSHI},
\item and finding relations between metrics and faults \autocite{LU} \autocite{SINGH} \autocite{DALLAL}.
\end{itemize}

In the present day there are no papers published with the form of `A Metrics Suite for Object Oriented Design'. I expect that this has
to do with the saturation on metric reseach and that it is simply not possible to publish a whole new suite of metrics.
In contrast to this, most papers on metrics use one or more metrics introduced by Chidamber and Keremer, which shows the
impact on the field.

\paragraph{}
To conclude, the paper is well structured and has a clear contribution. The research problem is clear. However the
approach tends to focus mainly on complexity metrics, the paper contains some aspects that could be described more explicitly,
and the metric definitions have some inconsistencies. However the presented data is solid.
As intended, the metrics can be used as indicators to prevent faults as Basili et al. \autocite{BASILI} showed, and
besides this the work is still used in modern research.
